A large-scale analysis of racial disparities in police stops across the

### 2019-06-12 lib/paper_results.Rmd
Add basic stats

TODO

```{r basic_numbers}
# TODO(danj/amyshoe)
```

@@

```{r veil_of_darkness-mod}
bind_rows(
  vod$dst$coefficients %>% 
    mutate(model = "DST: cities and counties"),  
  vod$cities$coefficients %>% 
    mutate(model = "Full year: cities"),
  vod$states$coefficients %>% 
    mutate(model = "Full year: states")
) %>% 
  select(model, is_dark, std_error, everything()) %>% 
  kable()

```
\newpage
\begin{center}
\section{Disparity Analysis}
\end{center}
\begin{center}
\subsection{Outcome test results}
\end{center}
```{r disparity-city-hit_rates-table}
kable(disp$city$outcome$results$aggregate_hit_rates)
```
```{r disparity-state-hit_rates-table}
kable(disp$state$outcome$results$aggregate_hit_rates)
```
\newpage
```{r disparity-city-hit_rates-plot, fig.height = 3, fig.width = 7}
disp$city$outcome$plots$aggregate
```
```{r disparity-state-hit_rates-plot, fig.height = 3, fig.width = 7}
disp$state$outcome$plots$aggregate
```

>>>>

We have collected and released a dataset of 
`r pfs$basic_counts$n_stops_collected` traffic stops carried out by 
`r pfs$basic_counts$n_states_collected` state patrol agencies and 
`r pfs$basic_counts$n_cities_collected` municipal police departments.

We analyzed a unique dataset detailing 
`r pfs$basic_counts$n_stops_analyzed` traffic stops carried out by 
`r pfs$basic_counts$n_states_analyzed` state patrol agencies and 
`r pfs$basic_counts$n_cities_analyzed` municipal police departments.

@@

```{r veil_of_darkness-mod}
bind_rows(
  vod$dst$coefficients %>% 
    mutate(model = "DST: cities and counties"),  
  vod$cities$coefficients %>% 
    mutate(model = "Full year: cities"),
  vod$states$coefficients %>% 
    mutate(model = "Full year: states")
) %>% 
  select(model, is_dark, std_error, everything()) %>% 
  kable()
```

\newpage

\begin{center}
\section{Search Disparity Analysis}
\end{center}

\begin{center}
\subsection{Outcome test results}
\end{center}

```{r disparity-city-hit_rates-table}
kable(disp$city$outcome$results$aggregate_hit_rates)
```
```{r disparity-state-hit_rates-table}
kable(disp$state$outcome$results$aggregate_hit_rates)
```
\newpage
```{r disparity-city-hit_rates-plot, fig.height = 3, fig.width = 7}
disp$city$outcome$plots$aggregate
```
```{r disparity-state-hit_rates-plot, fig.height = 3, fig.width = 7}
disp$state$outcome$plots$aggregate
```
